Determination of Center of Rotation \\ in Computed Tomography

### 2017-07-14 seminar_cor/seminar_cor_haegele.tex
new phantom, also fanbeam sinogram

\subsubsection{Parallel Beam}
The simplest geometry in CT (from a mathematical point of view) is the parallel beam geometry.
Here all rays are parallel that are emitted from the same side of the object.
\Cref{subfig:parallelbeam} shows a schematic of this geometry with the resulting signal.
%
\begin{figure}[!h]
\centering
\subfloat[Parallel Beam]{\includegraphics[width=0.58\linewidth]{img/parallel_beam_geometry}%
\label{subfig:parallelbeam}}
\hfil
\subfloat[Fan Beam]{\includegraphics[width=0.4\linewidth, trim=0 -6cm 0 0]{img/fanbeamgeometry}%
\label{fig_second_case}}
\caption{Parallel beam and fan beam geometry. In parallel beam the source moving perpendicular to the ray direction for sampling a 1-dimensional image (graph). In fan beam, rays are not perpendicular but instead emmited in fan blade form. $\gamma$ is the rotation angle at which the signal is obtained. \cite{Buzug2008_chap3,Buzug2008_chap4}} 
\label{fig:parallalandfanbeam}
\end{figure}

This projection geometry can be mathematically expressed with the Radon transform.
When we think of the object as a function of attenuation coefficients $f(x,y)$ and the measured signal as a function of projected coefficients $R(r,\gamma)$ where $r$ is the position on the detector and $\gamma$ is the rotation angle at which the signal is obtained, then
\begin{equation}
R(r,\gamma) = \int_{-\infty}^{\infty} f(r\;cos(\gamma) + t\;sin(\gamma), r\;sin(\gamma)-t\;cos(\gamma))\;dt.
\end{equation} 
The parameter $t$ is the position on the ray that hits the detector at $r$ and angle $\gamma$, which makes it clear that the projection $R(r,\gamma)$ is the integral along a ray through the object $f(x,y)$.
The sampling of an object in this fashion, results in a so called sinogram.
The contribution of a specific area of the object to the individual projections, follows a sinusoidal path along the $\gamma$-axis as can be seen in \cref{fig:sinogram_parallel}
%
\begin{figure}[!h]
\centering
\includegraphics[width=\linewidth]{img/phantomandradon.png}
\caption{
A \enquote{smilie} phantom and its corresponding sinogram with $\gamma~\in~[0^\circ,360^\circ]$.
An imaginary CT would have started with source on top and detector on bottom and then rotated clockwise around the phantom.
}
\label{fig:sinogram_parallel}
\end{figure}
%

@@

\subsubsection{Fan Beam}
A more practical geometry is the fan beam, in which a source emits a flat beam that extends to the sides (like a fan blade).

>>>>

\subsubsection{Parallel Beam}
The simplest geometry in CT (from a mathematical point of view) is the parallel beam geometry.
Here all rays are parallel that are emitted from the same side of the object.
\Cref{subfig:parallelbeam} shows a schematic of this geometry with the resulting signal.
%
\begin{figure}[!h]
\centering
\subfloat[Parallel Beam]{\includegraphics[width=0.58\linewidth]{img/parallel_beam_geometry}%
\label{subfig:parallelbeam}}
\hfil
\subfloat[Fan Beam]{\includegraphics[width=0.4\linewidth, trim=0 -6cm 0 0]{img/fanbeamgeometry}%
\label{subfig:fanbeam}}
\caption{Parallel beam and fan beam geometry. 
In parallel beam the source moving perpendicular to the ray direction for sampling a 1-dimensional image (graph). 
In fan beam, rays are not perpendicular but instead emmited in fan blade form. 
$\gamma$ is the rotation angle at which the signal is obtained. 
Figures from~\cite{Buzug2008_chap3,Buzug2008_chap4}}
\label{fig:parallalandfanbeam}
\end{figure}

This projection geometry can be mathematically expressed with the Radon transform.
When we think of the object as a function of attenuation coefficients $f(x,y)$ and the measured signal as a function of projected coefficients $R(r,\gamma)$ where $r$ is the position on the detector and $\gamma$ is the rotation angle at which the signal is obtained, then
\begin{equation}
R(r,\gamma) = \int_{-\infty}^{\infty} f(r\;cos(\gamma) + t\;sin(\gamma), r\;sin(\gamma)-t\;cos(\gamma))\;dt.
\end{equation} 
The parameter $t$ is the position on the ray that hits the detector at $r$ and angle $\gamma$, which makes it clear that the projection $R(r,\gamma)$ is the integral along a ray through the object $f(x,y)$.
The sampling of an object in this fashion, results in a so called sinogram.
The contribution of a specific area of the object to the individual projections, follows a sinusoidal path along the $\gamma$-axis as can be seen in \cref{fig:sinogram_parallel}
%
\begin{figure}[!h]
\centering
\includegraphics[width=\linewidth]{img/phantomandradon.png}
\caption{
A \enquote{smilie} phantom and its corresponding sinogram with $\gamma~\in~[0^\circ,360^\circ]$.
An imaginary CT would have started with source on top and detector on bottom and then rotated clockwise around the phantom to obtain the shown sinogram.
}
\label{fig:sinogram_parallel}
\end{figure}
%

@@

\subsubsection{Fan Beam}
A more practical geometry is the fan beam, in which a source emits a flat beam that extends to the sides (like a fan blade). 
\Cref{subfig:fanbeam} shows a schematic of this geometry.
Here the projection for a single rotation angle can be obtained at once.
